% !TEX encoding = UTF-8 Unicode
% ---------------------------------------
% References


% ---------------------------------------
% Bibliography Commands
\newcommand{\bibauthors}[1]{\textbf{#1}}
\newcommand{\bibtitle}[1]{\textit{#1}}
\newcommand{\bibpublication}[1]{\textnormal{#1}}


% ---------------------------------------
% Bibliography Content
\begin{thebibliography}{9}
\begin{latin}

% ---------------------------------------
% Direct References
\item[\rl{\textbf{
منابع مستقیم (مطالعه شده)
}}]

\bibitem{onlinelearningbubeck}
\bibauthors{ S\'ebastien Bubeck}. 
\bibtitle{Introduction to Online Optimization}.\\
\bibpublication{Princeton University - Department of Operations Research and Financial Engineering, 2011}

\bibitem{convexoptimization}
\bibauthors{Stephen Boyd, Lieven Vandenberghe}. 
\bibtitle{Convex Optimization}.\\
\bibpublication{Cambridge University Press, 2004}


\bibitem{ocprogrammingzinkevich}
\bibauthors{M. Zinkevich}. 
\bibtitle{Online Convex Programming and Generalized Infinitesimal Gradient Ascent}.\\
\bibpublication{Proceedings of the Twentieth International Conference on Machine Learning ICML, 2003}

\bibitem{problemofconceptdrifttsymbal}
\bibauthors{A. Tsymbal}
\bibtitle{The problem of concept drift: definitions and related work}.\\
\bibpublication{2004}

\bibitem{koltermaloof2003}
\bibauthors{J. Z. Kolter, M. A. Maloof}
\bibtitle{Dynamic Weighted Majority: An Ensemble Method for Drifting Concepts}.\\
\bibpublication{3rd IEEE Int. Conf. on Data Mining ICDM, 2003}

\bibitem{predictionlearninggames2006}
\bibauthors{N. Cesa-Bianchi, G. Lugosi}
\bibtitle{Prediction, Learning, and Games}.\\
\bibpublication{Cambridge University Press, 2006}

\bibitem{onlinelearningshwartz2011}
\bibauthors{S. Shalev-Shwartz}
\bibtitle{Online Learning and Online Convex Optimization}.\\
\bibpublication{Foundations and Trends in Machine Learning, Vol. 4, No. 2, 2011}


% ---------------------------------------
% Indirect References
\item[\rl{\textbf{
منابع غیرمستقیم (ارجاع به آن‌ها آورده شده)
}}]

% ---------------------------------------
% Indirect Refernces: Problem of Concept Drift - Tsymbal

\bibitem{ahaetal1991}
\bibauthors{D. W. Aha, D. Kibler, M. K. Albert}
\bibtitle{Instance-Based Learning Algorithms}.\\
\bibpublication{Machine Learning, 6(1), 1991}

\bibitem{cunninghametal2003}
\bibauthors{P. Cunningham, N. Nowlan, S. J. Delany, M. Haahr}
\bibtitle{A Case-Based Approach to Spam Filtering that Can Track Concept Drift}.\\
\bibpublication{Proceedings of ICCBR-2003 Workshop on Long-Lived CBR Systems, 2003}

\bibitem{harriessammut1998}
\bibauthors{M. B. Harries, C. Sammut, K. Horm}
\bibtitle{Extracting Hidden Context}.\\
\bibpublication{Machine Learning, 32(2), 1998}

\bibitem{hultenetal2001}
\bibauthors{G. Hulten, L. Spencer, P. Domingos}
\bibtitle{Mining Time-Changing Data Streams}.\\
\bibpublication{Proc. 7 th ACM SIGKDD Int. Conf. on Knowledge Discovery and Data Mining KDD, 2001}


\bibitem{widmerkubat1993}
\bibauthors{G. Widmer, M. Kubar}
\bibtitle{Effective Learning in Dynamic Environments by Explicit Context Tracking}.\\
\bibpublication{Proc. 6 th European Conf. on Machine Learning ECML, 1993}

\bibitem{klinkenberg2004}
\bibauthors{R. Klinkenberg}
\bibtitle{Learning drifting concepts: Example selection vs. example weighting}.\\
\bibpublication{Intelligent Data Analysis, Special Issue on Incremental Learning Systems Capable of Dealing with Concept Drift, 8 (3), 2004}

\bibitem{salganicoff1997}
\bibauthors{M. Salganicoff}
\bibtitle{Tolerating concept and sampling shift in lazy learning using prediction error context switching}.\\
\bibpublication{AI Review, Special Issue on Lazy Learning, 11 (1-5), 1997}

\bibitem{stanley2003}
\bibauthors{K. O. Stanley}
\bibtitle{Learning Concept Drift with a Committee of Decision Trees}.\\
\bibpublication{Technical Report AI03-302, Department of Computer Sciences, The University of Texas at Austin, 2003}

\bibitem{schlimmergranger1986}
\bibauthors{J. C. Schlimmer, R. H. Granger Jr.}
\bibtitle{Incremental Learning from Noisy Data}.\\
\bibpublication{Machine Learning, 1(3), 1986}

\bibitem{widmerkubat1996}
\bibauthors{G. Widmer, M. Kubat}
\bibtitle{Learning in the presence of concept drift and hidden contexts}.\\
\bibpublication{Machine Learning, 23 (1), 1996}

\bibitem{kubatwidmer1994}
\bibauthors{M. Kubat, G. Widmer}
\bibtitle{Adapting to drift in continuous domains}.\\
\bibpublication{European Conference on Machine Learning (ECML), 1995}

\bibitem{streetkim2001}
\bibauthors{W. N. Street, Y. Kim}
\bibtitle{A streaming ensemble algorithm (SEA) for large-scale classification}.\\
\bibpublication{Proc. 7th ACM SIGKDD Int. Conf. on Knowledge Discovery and Data Mining KDD, 2001}

\bibitem{wangetal2003}
\bibauthors{H. Wang, W. Fan, P. S. Yu, J. Han}
\bibtitle{Mining concept-drifting data streams using ensemble classifiers}.\\
\bibpublication{Proceeding KDD '03 Proceedings of the ninth ACM SIGKDD international conference on Knowledge discovery and data mining, 2003}

\bibitem{hemboldlong1994}
\bibauthors{D. P. Hembold, P. M. Long}
\bibtitle{Tracking drifting concepts by minimizing disagreements}.\\
\bibpublication{Machine Learning 14(1), 1994}

\bibitem{kuhetal1991}
\bibauthors{A. Kuh, T. Petsche, R. L. Rivest}
\bibtitle{Learning time-varying concepts}.\\
\bibpublication{Advances in Neural Information Processing Systems (NIPS) 3, Morgan Kaufmann, 1991}

\bibitem{lanquillonrenz1999}
\bibauthors{C. Lanquillon, I. Renz}
\bibtitle{Adaptive Information Filtering: Detecting Changes in Text Streams}.\\
\bibpublication{Proc. 8 th Int. Conf. on Information and Knowledge Management CIKM, 1999}

\bibitem{leakewilson1999}
\bibauthors{D. B. Leake, D. C. Wilson}
\bibtitle{When Experience is Wrong: Examining CBR for Changing Tasks and Environments}.\\
\bibpublication{Proc. 3 rd Int. Conf. on Case-Based Reasoning ICCBR, 1999}










%\bibitem{einstein} 
%Albert Einstein. 
%\textit{Zur Elektrodynamik bewegter K{\"o}rper}. (German) 
%[\textit{On the electrodynamics of moving bodies}]. 
%Annalen der Physik, 322(10):891–921, 1905.
 
%\bibitem{knuthwebsite} 
%Knuth: Computers and Typesetting,
%\\\texttt{http://www-cs-faculty.stanford.edu/\~{}uno/abcde.html}

\end{latin}
\end{thebibliography}